Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line

### 2024-03-21 manuscript_thev_transcriptome.tex
Put linebreaks in primer sequences of supp table to fit on pdf

\begin{longtable}[l]{|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{1.10in}|p{1.10in}|p{1.15in}}

@@

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Transcript\ ID}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Number\ of\ Exons}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Full\ Transcript}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 1}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 2}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 3}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 4}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 5}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 6}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 7}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Forward\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Reverse\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Agarose\ Gel}}}} \\

@@

\multicolumn{14}{>{\raggedright}m{\dimexpr 7.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\

@@

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-1655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTTCTGTTTGAATTGTGGGCGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-1.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

@@

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-1655}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGCCTGTTGGAATTGTTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCAGTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-2.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

>>>>

\begin{longtable}[l]{|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.35in}|p{0.60in}|p{0.60in}|p{1.15in}}

@@

\multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Transcript\ ID}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Region}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Number\ of\ Exons}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Full\ Transcript}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 1}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 2}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 3}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 4}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 5}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 6}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Exon\ 7}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Forward\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Reverse\ Primer}}}} & \multicolumn{1}{>{\cellcolor[HTML]{CFCFCF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textbf{Agarose\ Gel}}}} \\

@@

\multicolumn{14}{>{\raggedright}m{\dimexpr 6.2in+26\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{a}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ first\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{b}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ terminal\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{c}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Primer\ binds\ inside\ fourth\ exon}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{I}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_7\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{II}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 3\ exons\ of\ TRXPT\_10\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{III}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ last\ 4\ exons\ of\ TRXPT\_11\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{IV}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ dentical\ to\ TRXPT\_23\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{V}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_9\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{\textsuperscript{VI}}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{Agarose\ gel\ identical\ to\ TRXPT\_14\ due\ to\ identical\ splicing}}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{;\ }}} \\

@@

\multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{3}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-304}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1616-1655}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccTTCTGT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{TTGAATTGTGGGCGG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\cellcolor[HTML]{EFEFEF}\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-1.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\

@@

\multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{TRXPT\_2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{E1}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{2}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{54-1655}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{1964-2325}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.35in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{-}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCggtaccGAGGCCT}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTTGGAATTGTTGC}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{a}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.6in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{CCCtctagaCGTCCA}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\linebreak }}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{GTAGTCAGGAATTCTAGTG}}\textcolor[HTML]{000000}{\fontsize{3}{3}\selectfont{\textsuperscript{b}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.15in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}\includegraphics[width=1.1in, height=1in]{manuscript_thev_transcriptome_files/figure-latex/Supplementary PCR Methods-2.png}\textcolor[HTML]{000000}{\fontsize{4}{4}\selectfont{}}} \\
